Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-01-05 tex/test-WW-type-00s-PS.tex
alexei

@@

@@

In the Gauss Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$ 
has the form
\begin{subequations}\ba
	F_{LT}^{\cos(\phi_h -\phi_S)}(x,z,\Phperp) 
	&=& x\sum_q e_q^2\,g_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \\
	F_{LT}^{\cos(\phi_h-\phi_S)}(x,z,\la\Phperp\ra) 
	&=&  x\sum_q e_q^2\,g_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\;
	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
	\label{eq:asymmetry_g1t_pt-II}
\ea\end{subequations}
where 
$\lambda  = z^2 \avkperp_{g_{1T}^\perp} + \avpperp_{D_1}$,
$b^{(1)}_{\rm B} = 2M_N$,
$c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$,
see App.~\ref{App:convol-details} for details.
We remind that $g^{\perp q}_{1T}$ and the Sivers function are both 
constrained by the positivity bound \cite{Bacchetta:1999kz} 
\be
	\frac{\kperp^2}{M^2}\left( (g^{\perp q}_{1T}(x,\kperp^2))^2 
	+ (f_{1T}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 
\ee
so that one has
\be
\frac{f_{1}^{q}(x)^2}{16\pi M^2} - \frac{f_{1T}^{\perp q}(x)^2}{4\pi \avkperp_{f_{1T}^\perp} } -
\frac{g_{1T}^{\perp q}(x)^2}{4\pi \avkperp_{g_{1T}^\perp} } \ge 0
\label{eq:positivity}
\ee
see Fig.~\ref{g1t_pos}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/ALT_COMPASS_x.pdf}  
	\caption{\label{g1t_jlab} 
	$A_{LT}^{\cos(\phi_h -\phi_S)}$  as a function of $ x $  at typical kinematics 
	of COMPASS, 
	$\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
	\newline\PS{Can we compare here to COMPASS data from 
	\cite{Kotzinian:2007uv}?}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We assume Gaussian form for Kotzinian-Mulders function $h_{1L}^{\perp a}$:
\be
	h_{1L}^{\perp a}(x,\kperp^2) = h_{1L}^{\perp (1) a}(x)\,
	\frac{2 M^2}{\pi{\avkperp_{h_{1L}^\perp}^2}}\,e^{-\kperp^2/{\avkperp_{h_{1L}^\perp}^2}}
	\;,\label{eq:h1l_final}
\ee
We will use WW-type approximation from Eq.~(\ref{Eq:WW-approx-h1L}) 
for calculation of $h_{1L}^{\perp (1) a}(x)$ and for the estimates of the 
asymmetry $\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}} = 0.25$ (GeV$^2$).
Notice that the Kotzinian-Mulders function and $h^{\perp q}_{1L}$ obey the
positivity bound \cite{Bacchetta:1999kz}
\be
	\frac{\kperp^2}{M^2}\left( (h^{\perp q}_{1L}(x,\kperp^2))^2 + 
	(h_{1}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 \, .
\ee
so that one has
\be
\frac{f_{1}^{q}(x)^2}{16\pi M^2} - \frac{h_{1}^{\perp q}(x)^2}{4\pi \avkperp_{h_{1}^\perp} } -
\frac{h_{1L}^{\perp q}(x)^2}{4\pi \avkperp_{h_{1TL}^\perp} } \ge 0
\label{eq:positivity1}
\ee
which is plottde in Fig.~\ref{h1l_pos}. Notice that for $d$-quark the positivity is violated that may be due to the big Boer-Mulders $d$-quark function from Ref.~\cite{Barone:2015ksa}. As far as determination of the size of Boer-Mulders functions is far from ideal, we cautiously keep the present result. Future determinations of Boer-Mulders functions will help to clarify the issue of positivity constraints.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_COMPASS_x.pdf}  
	\caption{\label{aul_jlab} 
	$A_{UL}^{\sin(2\phi_h)}$  as a function of $ x $  at typical kinematics 
	of COMPASS, 
	$\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
	}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
\newpage
%========= SECTION 8: TWIST-3 IN WW-TYPE APPROXIMATION ===============
\section{Subleading twist asymmetries in WW-type approximation}
\label{Sec-7:twist-3-and-WW}

@@

In the WW-type approximation the structure function
$F_{LT}^{\cos\phi_S}$ is due to $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$ 
whose collinear counterparts are more or less well known, see
Secs.~\ref{Sec-3.4:WW-classic-experiment} and \ref{Sec-5.1:FUU-basis}.
Assuming the Gaussian Ansatz for $g_T^a(x,\kperp)$ yields for the
structure function 
\begin{subequations}\ba
	F_{LT}^{\cos\phi_S}(x,z,\Phperp) 
	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\,g_T^q(x)\,D_1^q(z)\;   
	{ \cal G}(\Phperp)\, , \label{Eq:FLTcosphiS-Gauss}\\
	F_{LT}^{\cos\phi_S}(x,z)
	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\, g_T^q(x)\,D_1^q(z)\, ,
\ea\end{subequations}
with the width $\lambda= z^2 \avkperp_{g_T} + \avpperp_{D_1}$
in the Gaussian ${\cal G}(\Phperp)$. We estimate $g_T^a(x)$ in terms 
of $g_1^a(x)$ according to Eq.~(\ref{Eq:WW-original1}) assuming for 
the Gaussian width $\avkperp_{g_T}=\avkperp_{g_1}$.\footnote{
	Notice that one could also proceed in a different way: 
	explore first the WW-type-relation (\ref{Eq:WW-type-5}), and
	assume then the Gauss Ansatz for $g_{1T}^{\perp}(x,\kperp)$ 
	according to (\ref{eq:g1t}). Solving then the convolution integral 
	yields a result different from (\ref{Eq:FLTcosphiS-Gauss})
	which depends much more strongly on Gaussian model parameters.
	The operations of applying the WW-type approximations and 
	employing the Gauss Ansatz do not commute in general.
	The solution presented in (\ref{Eq:FLTcosphiS-Gauss}) is 
	preferable as it helps to minimize model dependence.}

@@

The structure function $F_{UL}^{\cos\phi_h}$ reads
\begin{subequations}\ba
	F_{LL}^{\cos \phi_h}(x,z,\Phperp)
	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \, , \\ 
	F_{LL}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\;
	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\, , 
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{g_{L}^\perp} + \avpperp_{D_1}$, 
$b^{(1)}_{\rm B}=2M_N$,
$c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$, see App.~\ref{App:convol-details}.
We approximate the Gaussian width $\avkperp_{g_{L}^\perp}=\avkperp_{g_1}$ and 
estimate $g_L^{\perp(1) a}(x)$ according to Eq.~(\ref{Eq:WW-type-gLperp}) as
\be
	x\,g_L^{\perp(1) a}(x) = \frac{\la \kperp^2\ra_{g_1}}{2\,M_N^2}\,
	g_1^a(x) \,.
\ee
The asymmetries $A_{LL}^{\cos\phi_S}=F_{LL}^{\cos\phi_S}/F_{UU}$  for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{allcosphi_jlab}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.4\textwidth]{figs/ALLcosphi_x.pdf} 
\includegraphics[width=0.4\textwidth]{figs/ALLcosphi_PT.pdf}
\caption{\label{allcosphi_jlab} $A_{LL}^{\cos\phi_h}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The $F_{UT}^{\sin(\phi_h-\phi_S)}$ modulation of SIDIS cross section is related to  the Sivers function~\cite{Sivers:1989cc}, which describes the number density of unpolarized quarks inside a 
transversely polarized proton, has so far received the widest attention, 
from both phenomenological and experimental points of view.

The Sivers function $f_{1T}^\perp$ is related to initial and final state interactions of the struck quark and the rest of the nucleon and could not exist 
without the contribution of the orbital angular momentum of partons to the spin of the nucleon. 
As such it encodes the correlation between the partonic intrinsic motion and the transverse spin of the nucleon, and it generates a dipole deformation in momentum space.

Over the years, the Sivers function has been extracted from SIDIS data
by several groups, with consistent results 
\cite{Anselmino:2010bs,Anselmino:2005ea,Anselmino:2005an,Collins:2005ie,Vogelsang:2005cs,Anselmino:2008sga,Bacchetta:2011gx,Echevarria:2014xaa}.

@@

The $F_{UT}^{\sin(\phi_h+\phi_S)}$ modulation of the SIDIS cross section is due to convolution of the transversity distribution $h_1$, which is the only source of information on the tensor charge of the 
nucleon, and the Collins FF $H_1^\perp$, that decodes the fundamental correlation between
the transverse spin of a fragmenting quark and the transverse momentum
of the final produced hadron.

There are many extractions of $h_1$ and $H_1^\perp$ from a combined fit of SIDIS and $e^+e^-$ data, for instance those of Refs.~\cite{Anselmino:2013vqa,Kang:2014zza,Anselmino:2015sxa}.

@@

In the Gauss Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$ 
has the form
\begin{subequations}\ba
	F_{LT}^{\cos(\phi_h -\phi_S)}(x,z,\Phperp) 
	&=& x\sum_q e_q^2\,g_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \\
	F_{LT}^{\cos(\phi_h-\phi_S)}(x,z,\la\Phperp\ra) 
	&=&  x\sum_q e_q^2\,g_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\;
	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
	\label{eq:asymmetry_g1t_pt-II}
\ea\end{subequations}
where 
$\lambda  = z^2 \avkperp_{g_{1T}^\perp} + \avpperp_{D_1}$,
$b^{(1)}_{\rm B} = 2M_N$,
$c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$,
see App.~\ref{App:convol-details} for details.
We remind that $g^{\perp q}_{1T}$ and the Sivers function are both 
constrained by the positivity bound \cite{Bacchetta:1999kz} 
\be
	\frac{\kperp^2}{M^2}\left( (g^{\perp q}_{1T}(x,\kperp^2))^2 
	+ (f_{1T}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 
\ee
so that one has
\be
\frac{(f_{1}^{q}(x))^2}{16\pi M^2} - \frac{(f_{1T}^{\perp q}(x))^2}{4\pi \avkperp_{f_{1T}^\perp} } -
\frac{(g_{1T}^{\perp q}(x))^2}{4\pi \avkperp_{g_{1T}^\perp} } \ge 0
\label{eq:positivity}
\ee
see Fig.~\ref{g1t_pos}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/ALT_COMPASS_x.pdf}  
	\caption{\label{g1t_jlab} 
	$A_{LT}^{\cos(\phi_h -\phi_S)}$  as a function of $ x $  at typical kinematics 
	of COMPASS, 
	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$.
	\newline\PS{Can we compare here to COMPASS data from 
	\cite{Kotzinian:2007uv}?}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We assume Gaussian form for Kotzinian-Mulders function $h_{1L}^{\perp a}$:
\be
	h_{1L}^{\perp a}(x,\kperp^2) = h_{1L}^{\perp (1) a}(x)\,
	\frac{2 M^2}{\pi{\avkperp_{h_{1L}^\perp}^2}}\,e^{-\kperp^2/{\avkperp_{h_{1L}^\perp}^2}}
	\;,\label{eq:h1l_final}
\ee
We will use WW-type approximation from Eq.~(\ref{Eq:WW-approx-h1L}) 
for calculation of $h_{1L}^{\perp (1) a}(x)$ and for the estimates of the 
asymmetry $\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}} = 0.25$ (GeV$^2$).
Notice that the Kotzinian-Mulders function and $h^{\perp q}_{1L}$ obey the
positivity bound \cite{Bacchetta:1999kz}
\be
	\frac{\kperp^2}{M^2}\left( (h^{\perp q}_{1L}(x,\kperp^2))^2 + 
	(h_{1}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 \, .
\ee
so that one has
\be
\frac{(f_{1}^{q}(x))^2}{16\pi M^2} - \frac{(h_{1}^{\perp q}(x))^2}{4\pi \avkperp_{h_{1}^\perp} } -
\frac{(h_{1L}^{\perp q}(x))^2}{4\pi \avkperp_{h_{1TL}^\perp} } \ge 0
\label{eq:positivity1}
\ee
which is plottde in Fig.~\ref{h1l_pos}. Notice that for $d$-quark the positivity is violated that may be due to the big Boer-Mulders $d$-quark function from Ref.~\cite{Barone:2015ksa}. As far as determination of the size of Boer-Mulders functions is far from ideal, we cautiously keep the present result. Future determinations of Boer-Mulders functions will help to clarify the issue of positivity constraints.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_COMPASS_x.pdf}  
	\caption{\label{aul_jlab} 
	$A_{UL}^{\sin(2\phi_h)}$  as a function of $ x $  at typical kinematics 
	of COMPASS, 
	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$.
	}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
\newpage
%========= SECTION 8: TWIST-3 IN WW-TYPE APPROXIMATION ===============
\section{Subleading twist asymmetries in WW-type approximation}
\label{Sec-7:twist-3-and-WW}

@@

In the WW-type approximation the structure function
$F_{LT}^{\cos\phi_S}$ is due to $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$ 
whose collinear counterparts are more or less well known, see
Secs.~\ref{Sec-3.4:WW-classic-experiment} and \ref{Sec-5.1:FUU-basis}.
Assuming the Gaussian Ansatz for $g_T^a(x,\kperp)$ yields for the
structure function 
\begin{subequations}\ba
	F_{LT}^{\cos\phi_S}(x,z,\Phperp) 
	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\,g_T^q(x)\,D_1^q(z)\;   
	{ \cal G}(\Phperp)\, , \label{Eq:FLTcosphiS-Gauss}\\
	F_{LT}^{\cos\phi_S}(x,z)
	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\, g_T^q(x)\,D_1^q(z)\, ,
\ea\end{subequations}
{\color{blue} AP - I disagree with \ref{Eq:FLTcosphiS-Gauss} see my notes}
with the width $\lambda= z^2 \avkperp_{g_T} + \avpperp_{D_1}$
in the Gaussian ${\cal G}(\Phperp)$. We estimate $g_T^a(x)$ in terms 
of $g_1^a(x)$ according to Eq.~(\ref{Eq:WW-original1}) assuming for 
the Gaussian width $\avkperp_{g_T}=\avkperp_{g_1}$.\footnote{
	Notice that one could also proceed in a different way: 
	explore first the WW-type-relation (\ref{Eq:WW-type-5}), and
	assume then the Gauss Ansatz for $g_{1T}^{\perp}(x,\kperp)$ 
	according to (\ref{eq:g1t}). Solving then the convolution integral 
	yields a result different from (\ref{Eq:FLTcosphiS-Gauss})
	which depends much more strongly on Gaussian model parameters.
	The operations of applying the WW-type approximations and 
	employing the Gauss Ansatz do not commute in general.
	The solution presented in (\ref{Eq:FLTcosphiS-Gauss}) is 
	preferable as it helps to minimize model dependence.}

@@

The structure function $F_{UL}^{\cos\phi_h}$ reads
\begin{subequations}\ba
	F_{LL}^{\cos \phi_h}(x,z,\Phperp)
	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \, , \\ 
	F_{LL}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\;
	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\, , 
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{g_{L}^\perp} + \avpperp_{D_1}$, 
$b^{(1)}_{\rm B}=2M_N$,
$c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$, see App.~\ref{App:convol-details}.
We approximate the Gaussian width $\avkperp_{g_{L}^\perp}=\avkperp_{g_1}$ and 
estimate $g_L^{\perp(1) a}(x)$ according to Eq.~(\ref{Eq:WW-type-gLperp}) as
\be
	x\,g_L^{\perp(1) a}(x) = \frac{\la \kperp^2\ra_{g_1}}{2\,M_N^2}\,
	g_1^a(x) \,.
\ee
The asymmetries $A_{LL}^{\cos\phi_S}=F_{LL}^{\cos\phi_S}/F_{UU}$  for 
COMPASS are plotted in Fig.~\ref{allcosphi_jlab}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/ALLcosphi_COMPASS_x.pdf}  
	\caption{\label{allcosphi_jlab} 
	$A_{LL}^{\cos(\phi_h)}$  as a function of $ x $  at typical kinematics 
	of COMPASS, 
	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$.
	}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
